Nodal Discontinuous Galerkin Method for the Euler Equations of Fluid Dynamics

### 2017-07-11 Documents/Euler/dgEulerCurvilinear.tex
added figures to paper

@@

@@

\subsubsection{Shock-Entropy Wave Interaction}

>>>>

\usepackage{graphicx}
\graphicspath{ {Figures/} }

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{RiemannProblem_d5.png}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{RiemannProblem_v5.png} &
	  \includegraphics[width=.475\textwidth]{RiemannProblem_p5.png}
	\end{tabular}	
  \end{center}
  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the Riemann Problem at $t=0.012$, computed with 200 cells and the third order integration method (black), and the exact solution, obtained with Toro's Riemann solver (red).}
  \label{fig:Riemann}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{BlastD.png}	
	\begin{tabular}{cc}
     \includegraphics[width=.475\textwidth]{BlastV.png}
     \includegraphics[width=.475\textwidth]{BlastP.png}	
    \end{tabular}
  \end{center}
  \caption{Results showing the density (top), velocity (bottom left), and pressure (bottom right) for the Woodward-Collela blast wave problem at $t=0.038$, computed with the 400 cells (black) and 2000 cells (red).}
  \label{fig:Blast}
\end{figure}
\clearpage
\subsubsection{Shock-Entropy Wave Interaction}

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{den.png} &
	  \includegraphics[width=.475\textwidth]{denzoom.png}
	\end{tabular}
  \end{center}
  \caption{Results showing the density for the Shock Entropy Wave problem at $t=1.8$, computed with 200 cells (green) and 1000 cells (black).}
  \label{fig:shock}
\end{figure}
